---
title: "Developing Data Products W4"
author: "Xinyu GUO"
date: "2021/8/30"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
Peer-graded Assignment: Course Project: Shiny Application and Reproducible Pitch

This peer assessed assignment has two parts.

First, you will create a Shiny application and deploy it on Rstudio's servers.

Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

This coursework use the dataset of diamond 

## the code
Click the Below Link for the detailed code.

https://github.com/glorian1999/Developing-Data-Products-W4/tree/main

## Diamond Analysis Report

Diamond Data Analysis Report enabled developing data products using shiny apps being embeded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.

## Application Overview

- Diamonds Properties can be analysed using several Parameters.
- Carat,Price,sample size,color Depth are some of the common parameters.
- This Report enables to pick the right parameters for the best Diamond selection.

## Data Used
The data used for this application is diamonds data set, which is part of ggplot2 package. Containing information about 53940 diamonds with 10 variables.

```{r, echo=TRUE}
library("ggplot2")
head(diamonds)
```